---
title: "BelkinExploratoryAnalysis"
author: "KimN"
date: "11 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo=FALSE}
BelkinElagoComplete <- read.delim("C:/Users/kimne/Ubiqum/Module2/BelkinElagoComplete.csv")
```

## Exploration Belkin Data Set

This analysis serves the purpose to explore the Belkin Elago Data and to gather some first insights and relations on the data set.
Therefor, we take a look at the descriptive statistics in the first step.

### Descriptive statistics

```{r BelkinElagoComplete}
summary(BelkinElagoComplete)
str(BelkinElagoComplete)

summary(BelkinElagoComplete$salary)

summary(BelkinElagoComplete$age)

summary(BelkinElagoComplete$credit)
```

### Exploring relationships between variables

In a next step, we will figure out the relationships and correlations between variables using plots, correlation matrix and variances

```{r BelkinElagoComplete, echo=FALSE}
names(BelkinElagoComplete)<-c("salary","age","education","car","zip","credit","brand")
```
*Correlations

```{r BelkinElagoComplete}
correlation_table(data=BelkinData,target="salary")
correlation_table(data=BelkinData,target="credit")
```

## Plots and Histograms

```{r BelkinElagoComplete, echo=FALSE}
plot(BelkinElagoComplete$age,BelkinElagoComplete$salary)
hist(BelkinElagoComplete$credit)
```

Since there seems to be no meaningful connection between age and salary we are now going to explore the relationship between education level and salary, which is straighforward.

### Plotting education against salary

```{r BelkinElagoComplete, echo=FALSE}
ggplot(BelkinData,
       aes(education, salary)) + geom_jitter()

ggplot(BelkinData, 
  mapping = aes(x = education, y = salary)) + geom_jitter(aes(color = age))

ggplot(BelkinData,
       mapping=aes(x=education,y=salary))+
  geom_jitter(color=ifelse(BelkinData$age<=40, "red", "black"))

ggplot(BelkinData, 
  mapping = aes(x = education, y = salary)) + geom_jitter(aes(color = brand))

```

We can see that age does not affect salary in a crucially but education level does. Also it seems to be that Elago is somewhat more popular among well educated and good earning individuals.

### Explaining patterns in credit status

In a next step we will now take into account the credit variable in order to explore if credit status is affected by age, salary and education.

```{r BelkinElagoComplete, echo=FALSE}
ggplot(BelkinData, mapping = aes(x=age,y=credit)) +
  geom_point(aes(color = salary)) + facet_grid(~education)

ggplot(BelkinData, mapping = aes(x=age, y=credit, fill = salary)) +
  geom_bar(stat = "identity") + facet_wrap(~education)

ggplot(BelkinData, mapping = aes(x=salary, y=credit)) +
  geom_point(aes(color = age)) + facet_grid(~education)
```

### Boxplot analysis

Finally, we will investigate the density and ranges of credit status and age, devided by the brands Belkin and Elago, using boxplots.

```{r BelkinElagoComplete, echo=FALSE}
ggplot(BelkinData, mapping = aes(y=credit))+facet_wrap(~education)+geom_boxplot()

ggplot(BelkinData, mapping = aes(y=credit))+
  facet_wrap(~brand)+geom_boxplot()

ggplot(BelkinData, mapping = aes(y=age))+
  facet_wrap(~brand)+geom_boxplot()
```


