---
title: "Customer Brand Preferences"
author: "KimN"
date: "17 10 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In the following, we will evaluate the brand preferences of Blackwell´s customers using Random Forest Analysis. 
We will start by training and testing the model with the complete data set and then move on to predicting brand preferences.


Therefore, the following preparatory steps have been undertaken in advance.

*Loading data sets and libraries

```{r loading data, echo = FALSE, message=FALSE}

BelkinElagoComplete <- 
  read.delim("C:/Users/kimne/Ubiqum/Module2/BelkinElagoComplete.csv")

SurveyIncomplete <- 
  read.csv("C:/Users/kimne/Ubiqum/Module2/BrandPreferences/Data/SurveyIncomplete.csv")


library(caret)
library(mlbench)
library(dplyr)
```


*Renaming attributes

```{r naming, echo = FALSE}
names(BelkinElagoComplete) <- 
  c("salary","age","education","car","zip","credit","brand")

names(SurveyIncomplete) <- 
  c("salary","age","education","car","zip","credit","brand")
```


*Selecting subset of arrtributes, pre-processing

```{r pre-processing, echo = FALSE}
BelkinSmall <- BelkinElagoComplete %>% select("salary","age","education","brand")

Incomplete <- SurveyIncomplete %>% select("salary","age","education","brand")
```

```{r factoring, include = FALSE}
as.factor(BelkinSmall$brand)

as.factor(BelkinSmall$education)

as.factor(Incomplete$education)
```

*Data splitting

```{r data-splitting, include = FALSE}
inTrain <- createDataPartition(y=BelkinSmall$brand, 
                               p=0.75, list=FALSE)
str(inTrain)

training <- BelkinSmall[inTrain,]

testing <- BelkinSmall[-inTrain,]
```



```{r plot, echo = FALSE}
ggplot(BelkinSmall, aes(brand)) + geom_bar(fill = "lightgreen") + ggtitle("Distribution of brand choices in the complete data set") + xlab("brand choice")
```


## Training the Random Forest Model with the training data

```{r rf model, echo = FALSE}
grid = expand.grid(.mtry = c(2,3)) 

ctrl <- trainControl(method = "oob" ,
                     search = "grid",
                     classProbs = TRUE
                     )

rfFit <- train(brand~., data=training, 
                method="rf", 
                preProc=c("center","scale"),
                tuneGrid = grid,
                trControl=ctrl
               )

rfFit
```



## Checking RF Model performance by predicting on the test data set

```{r rf prediction, echo = FALSE}
rfPred <- predict(rfFit, newdata=testing, 
                   type="raw")  ## why raw? why does class not work ??

testing$brand_pred <- predict(rfFit, testing,
                              type = "raw")


table(rfPred)
```

## Checking prediction performance with Confusion Metrix

```{r conf.metrix rf, echo = FALSE}
cmrf <- confusionMatrix(rfPred, testing$brand)

print(cmrf)
```



# Final Brand Predictions


```{r rf model final, echo = FALSE}
grid = expand.grid(.mtry = c(2,3)) 

ctrl <- trainControl(method = "oob" ,
                     search = "grid",
                     classProbs = TRUE
                     )

rfFitFinal <- train(brand~., data=BelkinSmall, 
                method="rf", 
                preProc=c("center","scale"),
                tuneGrid = grid,
                trControl=ctrl
               )

ggplot(rfFitFinal) +
  ggtitle("Random Forest Model") +
  xlab("Number of Parameters")

rfFitFinal
```


```{r rf prediction final, echo = FALSE}
rfPredFinal <- predict(rfFitFinal, newdata=Incomplete, 
                   type="raw")  


Incomplete$brand_Pred <- predict(rfFitFinal, Incomplete)

table((rfPredFinal))

ggplot(Incomplete, aes(brand_Pred)) + geom_bar(fill = "lightgreen") + ggtitle("Prediction of customer`s brand preferences") + xlab("brand choice")
```
